%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,9pt]{extarticle} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
%\defaultfontfeatures{Mapping=tex-text}
%\setmainfont{Lora}
\setmainfont{Muli}
\setsansfont{Muli}
\setmonofont{Muli}
%\setmonofont[Scale=0.9]{Roboto Mono}

\usepackage{parskip}

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage{fullpage}

\usepackage{soul}

\usepackage[bookmarks]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\LARGE\bfseries\scshape\sffamily\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{8mm}{3mm} % Spacing around sections

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Weipeng He, Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{15pt}
\setlength{\headsep}{10pt}

\usepackage{enumitem}
\setitemize{itemsep=-.4em,leftmargin=2em}
\renewcommand\labelitemi{-}

\hyphenation{Tsinghua}
\newcommand{\ind}{\hspace*{1em}}

\setlength{\parskip}{12pt}

\begin{document}
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	NAME AND CONTACT INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
  {\Huge\bfseries\sffamily WEIPENG HE}

  Seattle, WA 98109 $\bullet$
  \href{mailto:heweipeng@gmail.com}{\texttt{heweipeng@gmail.com}} $\bullet$
  \texttt{(206) 209-7280} $\bullet$
  \url{www.linkedin.com/in/hwp0} 
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\begin{enumerate}[label={[\arabic*]}]
  \item Egocentric Audio-Visual Noise Suppression. \\
        Roshan Sharma, Weipeng He, Ju Lin, Egor Lakomkin, Yang Liu, Kaustubh Kalgaonkar, \\
        in \textit{2023 IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}
        [\href{https://doi.org/10.1109/ICASSP49357.2023.10095890}{doi}]

  \item Multi-task Neural Network for Robust Multiple Speaker Embedding Extraction. \\
        Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        in \textit{Proc. Interspeech 2021}
        [\href{https://doi.org/10.21437/Interspeech.2021-1769}{doi}]

  \item Neural Network Adaptation and Data Augmentation for Multi-Speaker Direction-of-Arrival Estimation. \\
        Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        \textit{IEEE/ACM Transactions on Audio, Speech, and Language Processing}, vol. 29, pp. 1303–1317, 2021
        [\href{https://doi.org/10.1109/TASLP.2021.3060257}{doi}]

  \item IEEE SLT 2021 Alpha-mini Speech Challenge: Open Datasets, Tracks, Rules and Baselines. \\
        Yihui Fu, Weipeng He, et al. \\
        in \textit{2021 IEEE Spoken Language Technology Workshop (SLT)}
        [\href{https://doi.org/10.1109/SLT48900.2021.9383546}{doi}]

  \item Spatial attention for far-field speech recognition with deep beamforming neural networks. \\
        Weipeng He, Lu Lu, Biqiao Zhang, Jay Mahadeokar, Kaustubh Kalgaonkar, and Christian Fuegen, \\
        in \textit{2020 IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}
        [\href{https://doi.org/10.1109/ICASSP40776.2020.9053439}{doi}]

  \item The MuMMER Data Set for Robot Perception in Multi-Party HRI Scenarios. \\
        Olivier Canevet, Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        in \textit{2020 29th IEEE International Conference on Robot and Human Interactive Communication (RO-MAN)}

  \item Adaptation of multiple sound source localization neural networks with weak supervision and domain-adversarial training. \\
        Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        in \textit{2019 IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}
        [\href{https://doi.org/10.1109/ICASSP.2019.8682655}{doi}]

  \item MuMMER:\@ Socially intelligent human-robot interaction in public spaces. \\
        Mary Ellen Foster, Weipeng He, et al. \\
        in \textit{Proc.\ AI-HRI 2019}
        [\href{https://arxiv.org/abs/1909.06749}{preprint}]

  \item Joint localization and classification of multiple sound sources using a multi-task neural network. \\
        Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        in \textit{Proc. Interspeech 2018}
        [\href{http://doi.org/10.21437/Interspeech.2018-1269}{doi}, \href{https://www.youtube.com/watch?v=O7bQvg03RTc}{video}]

  \item Deep neural networks for multiple speaker detection and localization. \\
        Weipeng He, Petr Motlicek, and Jean-Marc Odobez, \\
        in \textit{2018 IEEE International Conference on Robotics and Automation (ICRA)}
        [\href{http://doi.org/10.1109/ICRA.2018.8461267}{doi}, \href{https://www.youtube.com/watch?v=_4EwuVlE_pU}{video}]

  \item Multimodal object recognition from visual and audio sequences. \\
        Weipeng He, Haojun Guan, and Jianwei Zhang, \\
        in \textit{2015 IEEE Int.\ Conf.\ on Multisensor Fusion and Information Integration for Intelligent Systems (MFI)}

  \item What to do first: the initial behavior in a multi-sensory household object recognition and categorization system. \\
        Haojun Guan, Weipeng He, and Jianwei Zhang, \\
        in \textit{2014 IEEE Int.\ Conf.\ on Multisensor Fusion and Information Integration for Intelligent Systems (MFI)}

  \item THUNLP at TAC KBP 2011 in entity linking. \\
        Yu Zhao, Weipeng He, Zhiyuan Liu, and Maosong Sun, \\
        in \textit{Proceedings of TAC, 2011}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	update date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vfill
\centering \footnotesize \itshape{Updated on \today}

\end{document}

