\documentclass[a4paper,14pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% Font
\usepackage{fontspec}
\setmainfont[Scale=1.4]{PT Sans Narrow}

% Footnote Symbol
\usepackage[symbol*]{footmisc}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

  \newcommand{\resheading}[1]{\vspace{5pt}{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.8in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\resbitem}[3]{
\item
\begin{tabular*}{6.8in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} #2 & \textit{#3} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\rescitem}[2]{
\item
\begin{tabular*}{6.8in}[t]{l l}
  \begin{tabular*}{1.5in}{l@{:}} #1 \\ \end{tabular*}
  & #2 \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
\textbf{\Huge Weipeng He} \vspace{6pt} & \\
Hagenbeckstr 60 & heweipeng@gmail.com \\
Hamburg, 22527 Germany & +49-176-7580-6525 \\
\end{tabular*}
\\

\vspace{2mm}

\resheading{Education}

\begin{itemize}
\item
	\ressubheading{University of Hamburg}{Hamburg, Germany}
		{M.Sc. in Intelligent Adaptive System}{Oct. 2012 - Present}
\begin{itemize}
    \resitem{GPA: 1.50\footnote{According to German university grading scale, grade is given from 1.0 to 5.0 with 1.0 the best. 1.5 is equivalent to ``outstanding''.}}
\end{itemize}

\item
\begin{tabular*}{6.8in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Tsinghua University} & Beijing, China \\
		\textit{Bachelor in Computer Science and Technology} & \textit{Aug. 2008 - Jul. 2012} \\
		\textit{Bachelor in Mathematics (second major)} & \textit{Sep. 2009 - Jul. 2012} \\
\end{tabular*}\vspace{-6pt}
\begin{itemize}
  \resitem{GPA: 89/100; Rank: 11/117}
\end{itemize}
\end{itemize}

\resheading{Experience}

\begin{itemize}
  \item
    \ressubheading{Technical Aspects of Multimodal Systems Group}{University of Hamburg}
    {Research Assistant}{Oct. 2012 - Present}
    \begin{itemize}
        \resitem{Implemented an visual-audio object recognition system using hidden Markov model\footnotemark.}
        \resitem{In addition to classifying an object, the system is also able to recognize the material of the object according to the sound.}
        \footnotetext{Example projects can be found in my GitHub repos: notGHMM, gval and interactiveOR in \texttt{https://github.com/hwp} .}
    \end{itemize}
\end{itemize}

\begin{itemize}
\item
	\ressubheading{Hulu (Beijing) Software Corporation}{Beijing, China}
		{Internship}{Jun. 2012 - Sep. 2012}
    \begin{itemize}
        \resitem{Improved search engine with fast approximate string matching.}
    \end{itemize}
\end{itemize}


\begin{itemize}
  \item
    \ressubheading{Intelligent Information Acquisition Group}{Tsinghua University}
    {Research Assistant}{Feb. 2012 - Jul. 2012}
    \begin{itemize}
        \resitem{Developed a dialogue system with reinforcement learning.}
    \end{itemize}
\end{itemize}

\begin{itemize}
  \item
    \ressubheading{Nature Language Processing Group}{Tsinghua University}
    {Research Assistant}{Apr. 2010 - Jan. 2012}
    \begin{itemize}
        \resitem{Explored novel methods of using Wikipedia knowledge for keyword extraction and word sense disambiguation.}
    \end{itemize}
\end{itemize}

\resheading{Skills}

\begin{itemize}
    \resbitem{Programming Languages\footnotemark:}{C, Java, C++, Python, Matlab.}{}
    \footnotetext{Languages are listed in a descending order of proficiency.}
    \resbitem{Libraries:}{Gstreamer, OpenCV, GSL.}{}
    \resbitem{Tools:}{Vim, Bash scripts, LaTeX.}{}
    \resbitem{Languages:}{Chinese (native speaker), English (fluent), German (beginner).}{}
\end{itemize}

\resheading{Scholarship and Awards}

\begin{itemize}
    \resbitem{Merit scholarships for international students ,}{University of Hamburg.}{Oct. 2013 - Mar. 2015}
    \resbitem{Outstanding Graduate,}{Tsinghua University.}{Jul. 2012}
\end{itemize}

\end{document}
